---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# opat

<!-- badges: start -->
<!-- badges: end -->

The goal of opat is to provide access to data and functions for assessing the performance and impacts of pest management strategies. OPAT stands for 'online performance assessment tool' and was developed as part of the European Horizon project ADOPT-IPM.

## Installation

You can install the development version of opat from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("vanichols/opat")
```

## Example

This is a basic example demonstrating a function to visualize pesticide loads, as calculated using Vandevoorde et al. (in revision). Here we look at a compound that has been banned in the European Union, diquat:

```{r example}
library(opat)
make_rose_plot(compound_name = "diquat",
              data = opat_hpli)
```

We can compare it to the Bordeaux mixture, which is used to control fungal and bacterial diseases:

```{r}
make_rose_plot_pair(
  compound_name1 = "diquat",
  compound_name2 = "Bordeaux mixture",
  data = opat_hpli)
```

We can also see what the current science says about glyphosate:

```{r}
make_rose_plot(compound_name = "glyphosate",
              data = opat_hpli)
```
