---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ADOPTpkg

<!-- badges: start -->
<!-- badges: end -->

The goal of ADOPTpkg is to provide access to data and functions for assessing the performance and impacts of pest management strategies.  It was developed as part of the European Horizon project ADOPT-IPM. There is a sister ShinyApp tool which provides an online interface.

## Installation

You can install the development version of ADOPTpkg from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("vanichols/ADOPTpkg")
```

## Example

This is a basic example demonstrating a function to visualize pesticide loads, as calculated using Vandevoorde et al. (in revision). Here we look at a compound that has been banned in the European Union, diquat:

```{r example}
library(ADOPTpkg)
adopt_Make_Rose_Plot(compound_name = "diquat",
              data = adopt_hpli)
```

We can compare it to the Bordeaux mixture, which is used to control fungal and bacterial diseases:

```{r}
adopt_Make_Distribution_Plot(
  compound_names = c("diquat", "Bordeaux mixture"),
  data = adopt_hpli)
```

If you fill out the questionaire, you can see the performance of the strategies in six areas:

```{r}
adopt_Make_Paired_Ridge_Plots(data = adopt_example)
```


You can also overlap the performances of the two strategies for easy comparison:

```{r}
adopt_Make_Overlapping_Ridge_Plots(adopt_example)
```

